Monte-Carlo-based design of a new sampling calorimeter toward the measurement of incident angle

### 2021-07-19 paper.tex
Updates

\newcommand{\pp}{\mbox{$pp$}\xspace}
\newcommand{\pAu}{\mbox{$p$+Au}\xspace}
\newcommand{\pPb}{\mbox{$p$+Pb}\xspace}
\newcommand{\pythia}{\textsc{Pythia8}\xspace}
\newcommand{\deta}{\mbox{$\Delta\eta$}\xspace}
\newcommand{\dphi}{\mbox{$\Delta\varphi$}\xspace}
\newcommand{\pt}{\mbox{$p_{\mathrm{T}}$}\xspace}
\newcommand{\pT}{\mbox{$p_{T}$}\xspace}
\newcommand{\Nch}{\mbox{$N_\mathrm{ch}$}\xspace}
\newcommand{\pythiae}{\pythia\ensuremath{~\mathrm{default}}}
\newcommand{\pythiashoving}{{\pythia\ensuremath{~\mathrm{String}~}}\ensuremath{\mathrm{Shoving}}}
\newcommand{\sonly}        {\ensuremath{\sqrt{s}}}

\begin{document}
\setcounter{page}{0}
\title[]{Exploring the string shoving model in PYTHIA8 \\for collective behaviors in $pp$ collisions}
\author{Junlee \surname{Kim}}
\email{junlee.kim@cern.ch}
\author{Eun-Joo \surname{Kim}}
\affiliation{Division of Science Education, Jeonbuk National University, Jeonju 54896}
\author{SuJeong \surname{Ji}}
\author{SangHoon \surname{Lim}}
\email{shlim@pusan.ac.kr}
%\thanks{Fax: +82-2-554-1643}
\affiliation{Department of Physics, Pusan National University, Busan 46241}

@@

\begin{abstract}
Two-particle correlations have been used to study property of a produced medium called Quark-Gluon Plasma (QGP) in relativistic heavy-ion collisions, and a long-range correlation among produced particles has been considered as a strong evidence of strongly interacting QGP. 
Strikingly, clear long-range correlations have been also observed in small collision systems like $pp$ and $p$+$A$ at a wide range of collision energies. 
%Several theoretical approaches have been proposed, but results in small collision systems have not fully understood yet.
A model introducing a repulsive force between flux tubes called string shoving can qualitatively describe the long-range near-side correlations in high multiplicity $pp$ collisions. 
This model implemented in the \pythia Monte Calro event generator allows us to perform detailed study.
In this work, a full data analysis to calculate associated yields and flow coefficients is performed with \pythia events, and the results are compared with experimental results.
We find that the string shoving model overestimates long-range near-side correlations particularly in low multiplicity events.
We also introduce a method to subtract such overestimated correlations in low multiplicity to have a more relevant comparison with the data. 
%Further study reveals that the string shoving model also generates the repulsive force in jet fragments. We also introduce a method to subtract such overestimated correlations and find that the predictions from the string shoving  after the subtraction are more comparable with the experimental results.

@@

\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
\keywords{String shoving, Collectivity, $pp$ collision}
\maketitle

\input{sec_intro.tex}
\pagebreak
\input{sec_ana.tex}
\pagebreak
\input{sec_results.tex}
\input{sec_summary.tex}

@@

\begin{acknowledgments}
%The authors would like to thank for useful discussions and a careful reading of the manuscript. 
%J. Kim and E.-J. Kim acknowledge support from the... .
S.J. Ji and S.H. Lim acknowledge support from a 2-Year Research Grant of Pusan
National University.
%The authors would like to thank Mr. Kim for helpful discussions and
%gratefully acknowledge support by MOCIE through National R$\&$D
%Project for Nano Science and Technology. C. H. C. and W. J. J.
%acknowledge the financial support by MOE through BK21 fellowships.
\end{acknowledgments}

>>>>

\newcommand{\XGB}{XGBoost}

\begin{document}
\setcounter{page}{0}
\title[]{ Monte-Carlo-based design of a new sampling calorimeter toward the measurement of incident angle }

\author{YoungJun \surname{Kim}}
\affiliation{Department of Physics, Korea University, Seoul 02841}
\author{Junlee \surname{Kim}}
\email{junlee.kim@cern.ch}
\author{Eun-Joo \surname{Kim}}
\affiliation{Department of Physics education, Jeonbuk National University, Jeonju 54896}
\author{GeiYoub  \surname{Lim}}
\affiliation{IPNS/KEK Tshukuba, Jaoan 305-0801}

@@

\begin{abstract}
THIS IS ABSTRACT

@@

%\pacs{68.37.Ef, 82.20.-w, 68.43.-h}
%\keywords{String shoving, Collectivity, $pp$ collision}
\maketitle

\section{Motivation}
\label{sec:mot}

\section{Analysis method}
\label{sec:ana}

\section{Results}
\label{sec:res}

\section{Conclusions}
\label{sec:con}

@@

\begin{acknowledgments}
\end{acknowledgments}
